gtsummary

### 2020-12-09 rmarkdown-gtsummary.Rmd
i nprogress

```{r, echo=TRUE}
tbl_summary_2 <-
  trial %>%
  select(age, grade, response, trt) %>%
  tbl_summary(by = trt,
              label = age ~ "Patient Age",
              statistic = list(all_continuous() ~ "{mean} ({sd})",
                               all_categorical() ~ "{n} / {N} ({p}%)"),
              digits = list(age ~ 2, 
                            all_categorical() ~ c(0, 0, 1)),
              missing = "no")
```

@@

>>>>

```{r, echo=TRUE}
tbl_summary_2 <-
  trial %>%
  select(age, grade, response, trt) %>%
  tbl_summary(
    by = trt,
    label = age ~ "Patient Age",
    statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n} / {N} ({p}%)"),
    digits = list(age ~ 2, 
                  all_categorical() ~ c(0, 0, 1)),
    missing = "no"
  )
```

@@

```{r, echo=TRUE}
tbl_summary_3 <-
  trial %>%
  select(age, grade, response, trt) %>%
  tbl_summary(by = trt, missing = "no") %>%
  add_p(test = all_continuous() ~ "t.test",
        pvalue_fun = ~style_pvalue(., digits = 2)) %>%
  add_n()
```

```{r, echo=FALSE, include = FALSE}
tbl_summary_3 %>% 
  as_gt() %>%
  gtsave(file = "summary_plus_plus.png")
```
